Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-26 Ben_Manuscripts/Paper1/Outline.tex
More organization

  We will now address the questions raised in the introduction in the order
  that they were asked.  %BJC: I dont like this

@@

  To discern the composition of the monomer layers, addressing (2), we ran 
  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
  \begin{itemize}
  	\item Both the sandwiched and parallel displaced configurations were tested.
	\item All systems are stable after 50 ns of simulation.  % BJC: edited this for clarity
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
        %MRS: remind people where the uncertainty comes from.
	%BJC: It looks like the 7 and 8 monomer systems were only run for 50 ns. The 4 monomer system was run for 200 ns. 5 and 6 have a lot of data. 7 and 8 flattened pretty quickly, so at the time I figured it wasn't worth continuing. But I'll extend them just to be thorough.
	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
	Systems built with 5 monomers in each layer equilibrate to a pore spacing
	that is most consistent with the experimental value of 4.12 nm derived from
	SAXS measurements (Figure~\ref{fig:SAXS}).
	\item The remainder of this discussion will focus on the analysis of systems
	built with 5 monomers per layer. 
  \end{itemize}

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  		   & \multicolumn{2}{c}{Starting Configuration} \\
  \hline
  Monomers per layer & Sandwiched & Parallel Displaced \\
  \midrule
  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing 
  %MRS added
  (given in \angstrom~)
  of the model increases as number of monomers
  in each layer increases. The pore spacing of a system starting in the 
  sandwiched configuration is systematically lower than that started in an 
  offset configuration. Systems built with 5 monomers per layer in a parallel
  displaced configuration result in a pore spacing closest 
  %MRS: clarified.
  %to experimental data
  to the experimental 4.12 \angstrom~}\label{table:p2p} 
  \end{table}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5layered.png}
		\caption{}\label{fig:zdf_layered}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{zdf5offset.png}
		\caption{}\label{fig:zdf_offset}
	\end{subfigure}
	\caption{Pair distribution functions of aromatic carbons for the
	(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, 
	parallel displaced configurations. 
        %MRS: added some info.
        Clear periodic maxima in the $z$ probability density indicate
        % Spikes in the distribution mark
	distinct layers. The magnitude of the spikes with respect to the 
	average suggest that the 5 monomer per layer, sandwiched configuration
	possesses a higher degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

  To answer question (3) we require high resolution experimental evidence which we 
  can match to our simulations. Experimental WAXS measurements encode all structural
  details and we would like to match them as well as possible. 
  %MRS: also encodes the pore spacing
  %BJC: got rid of 'remaining' in 'remaining structural details'
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-$\pi$.
        %MRS: why R in R-pi? for reflection?
	%BJC: yes, R = reflection
	\item A weak intensity line is located at exactly half the $q_z$ value of
	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom$^-1$. The real space separation 
	corresponds to 4.5 \angstrom~ which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}[t]{0.47\linewidth}
		\centering
		\raisebox{.2\textwidth}{%
		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
		}
		\caption{}\label{fig:WAXS}
	\end{subfigure}
	\begin{subfigure}[t]{0.43\linewidth}
		\centering
	%	\vspace{12mm}
		\includegraphics[width=\linewidth]{SAXS.png}
		\caption{}\label{fig:SAXS}
	\end{subfigure}
	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
        %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
	%BJC: 1D is from a Yale paper. I'm going to remake the figure from the raw data but will reference that
	%BJC: The simulated 1D shows the right peaks, but the resolution makes it kind of pointy. I'll let you take a look at it but maybe it belongs in the supplemental
  \end{figure}

  In addition to the parallel displaced and sandwiched configurations we observed
  that the initial distance between layers can influence the approach towards 
  equilibrium.
  \begin{itemize}
  	\item Our choice of distance between layers results in long-term stability of 
	qualitatively different configurations suggesting that we have found more than
        one metastable free energy basin.
  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
	structure.
        \item We will refer to this large set of configurations, with an open pore, as 
        Basin OP (open pore) (Figure~\ref{fig:abasin}).
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom~ apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
	\item This will be called Basin CP (closed pore) (Figure~\ref{fig:bbasin}).
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.
  \end{itemize}

@@

  We created systems using three 
  distinct initial configurations and examined their structure by simulating 
  X-ray diffraction patterns produced from equilibrated MD trajectories.
  \begin{itemize}
  	\item Systems were built in both the parallel displaced and sandwiched 
	configurations with an intial layer spacing of 3.7 \angstrom~.
	\item A third system was created by stacking layers in the sandwiched 
	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
	\item For ease of reference, the third system will be referred to as Basin D (disordered). 
	\item The three systems were equilibrated according to our procedure with
	NPT simulations of greater than 400 ns.
	\item Simulated diffration patterns were generated using portions of the
	trajectory after equilibration.  
	\item We assume the simulation has equilibrated when the distance between 
	pores and the membrane thickness stopped changing.
	\item Simulated diffraction patterns for all three structures are shown in 
	Figure ~\ref{fig:XRDsim}. 
  \end{itemize}

  % Three paragraphs instead here? Talk about disordered, parallel displaced and 
  % layered separately? Try it. 
  % Talk about disordered last so it leads in to 
  % Also maybe don't talk about question 4 until after this
  Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  patterns shows the most consistency with the offset configuration in the OP basin.
  \begin{itemize}
        \item The disordered pore structure exhibits R-alkanes and R-pores but R-helix,
	R-$\pi$ and R-spots are not present. 
        \item Simulated XRD of the sandwiched configuration contains all features 
        except for R-helix.
        \item Most notably, R-spots appears in the expected location, which suggests 
        that there is something intrinsic to the sandwiched packing that gives rise 
        to such features.

	\item The equilibrated parallel displaced structure exhibits R-alkanes and
	R-pores in the expected locations. 
	\item Due to low resolution, making out the individual spots of R-pores is
	challenging and can be validated with slightly better resolution upon full
	spherical integration of the 3D structure factor. However, the same 
	information can be extracted by measuring the pore spacing as described earlier.
	\item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
	in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as 
	opposed to 3.7 \angstrom~.
	\item R-helix and R-spots are also both missing.
	\item The line which intersected both of these features in the restrained 
	simulations faded upon equilibration which suggests that monomers in the 
	parallel-displaced configuration may not give rise to the experimental WAXS 
	pattern seen.
	\item Simulated XRD of the sandwiched configuration contains all features 
	except for R-helix.
	\item Most notably, R-spots appears in the expected location, which suggests 
	that there is something intrinsic to the sandwiched packing that gives rise 
	to such features. 
  \end{itemize}

@@

  The spots that appear in the simulated XRD pattern of OP basin
  conformations are a result of the way alkane tails pack together.
  \begin{itemize}
  	\item Previously, the spots in the diffraction pattern had been explained 
	as the product of tilted alkane chains.
	\item We measured the tilt angle of the alkane chains and showed that our 
	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
	\item To understand the origin of the spots, we determined which atoms gave rise to the feature.i
	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
        that the spots arise as a consequence of the tails. 
	\item By removing atoms from the trajectory and simulating a diffraction 
	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
	\item Since the tails stay nearly flat, we plotted the centroids of the 
	tails and measured the angle between each centroid and its nearest neighbors
	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
	\item The distribution of these angles is consistent with the location of 
	the spots (Figure~\ref{fig:tail_packing}).
	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
	of spots are located on the simulated patterns (See Supplemental Information for quantitative proof)
	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
        and found the angle at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which 
        is a reconcilable difference with our simulated results.  
  \end{itemize}

>>>>

  We will now address the questions raised in the introduction in the order
  that they were asked.  %BJC: Not a fan of this

@@

  % BJC: might replace with a figure containing alllllll of the zdf's
  \begin{figure}[!ht]
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf5layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf5offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
        \caption{Pair distribution functions of aromatic carbons for the
        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
        parallel displaced configurations. Clear periodic maxima in the 
        $z$ probability density indicate distinct layers. The magnitude 
        of the spikes with respect to the average suggest that the 5 
        monomer per layer, sandwiched configuration possesses a higher 
        degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

  To discern the composition of the monomer layers, addressing (2), we ran 
  simulations of systems created with 4 - 8 monomers per layer.  % BJC: can't figure out how to word this : should be 'with between 4 and 8 monomers' or 'with from 4 to 8 monomers'?
  \begin{itemize}
  	\item Both the sandwiched and parallel displaced configurations were tested.
	\item All systems are stable after 400 ns of simulation.  % BJC: edited this for clarity
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
	%BJC: Working on getting them all run out to 400 ns
	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
	\item Systems built with 5 monomers in each layer equilibrate to a pore spacing
	that is most consistent with the experimental value of 4.12 nm derived from
	SAXS measurements (Figure~\ref{fig:SAXS}).
	\item The remainder of this discussion will focus on the analysis of systems
	built with 5 monomers per layer. 
  \end{itemize}

  % BJC: Even though I will shift focus to only 5 monomers per layer, I can put other data
  % such as XRD of 4, 6, 7, 8 mon/layer in supplemental information

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  		   & \multicolumn{2}{c}{Starting Configuration} \\
  \hline
  Monomers per layer & Sandwiched & Parallel Displaced \\
  \midrule
  4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
  5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
  6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
  7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
  8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing (given in $\nm$) of the model increases as
  number of monomers in each layer increases. The pore spacing of a system
  starting in the sandwiched configuration is systematically lower than 
  that started in an offset configuration. Systems built with 5 monomers
  per layer in a parallel displaced configuration result in a pore spacing
  closest to the experimental 4.12 $\nm$~}\label{table:p2p} 
  \end{table}

%  To answer question (3) we require high resolution experimental evidence which we 
%  can match to our simulations. Experimental WAXS measurements encode all structural
%  details and we would like to match them as well as possible. 
%  %MRS: also encodes the pore spacing
%  %BJC: got rid of 'remaining' in 'remaining structural details'
%  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
%  \begin{itemize}
%  	\item There are five major features present in the 2D experimental 
%	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
%	\item The first is located at $q_z$ = 1.7 \angstrom$^-1$,
%	corresponding to a real spacing of 3.7 \angstrom~. The reflection is 
%	attributed to $\pi$-$\pi$ stacking between aromatic rings in the direction
%	perpendicular to the membrane plane, or z-axis. For simplicity, this 
%	reflection will be referred to as R-$\pi$.
%       %MRS: why R in R-pi? for reflection?
%	%BJC: yes, R = reflection
%	\item A weak intensity line is located at exactly half the $q_z$ value of
%	R-$\pi$ ($q_z$ = 0.85 \angstrom$^-1$), corresponding to a 
%	real space periodic spacing of 7.4 \angstrom~. This reflection has been 
%	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
%	along the z axis meaning if the positions of the aromatic rings can
%	be traced by a helix, then for each turn in the helix, there should be
%	two aromatic rings. For this reason it will be referred to as R-helix.
%	\item A third major reflection is marked by a low intensity ring located
%	at r = 1.4 \angstrom$^-1$. The real space separation 
%	corresponds to 4.5 \angstrom~ which is characteristic of the average 
%	spacing between packed alkane chains. This reflection will be called R-alkanes.
%	\item Within R-alkanes, are four spots of higher intensity which 
%	will be called R-spots. All are located $\approx 40$ degrees from the $q_z$ axis
%	in their respective quadrants. In many liquid crystal systems this can be
%	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
%	\item The final major reflections correspond to the spacing and symmetry of 
%	the d\textsubscript{100} plane which can be related to the distance between
%	pores. The feature, which will be called R-pores, is characterized by dots 
%	along $q_z$ = 0. The spacing between dots is indicative of the hexagonal 
%	symmetry of the packed pores. It is easiest to interpret the data by 
%	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
%  \end{itemize}

%  \begin{figure}[!ht]
%	\centering
%	\begin{subfigure}[t]{0.47\linewidth}
%		\centering
%		\raisebox{.2\textwidth}{%
%		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
%		}
%		\caption{}\label{fig:WAXS}
%	\end{subfigure}
%	\begin{subfigure}[t]{0.43\linewidth}
%		\centering
	%	\vspace{12mm}
%		\includegraphics[width=\linewidth]{SAXS.png}
%		\caption{}\label{fig:SAXS}
%	\end{subfigure}
%	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
%	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
%	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
        %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
	%BJC: 1D is from a Yale paper. I'm going to remake the figure from the raw data but will reference that
	%BJC: The simulated 1D shows the right peaks, but the resolution makes it kind of pointy. I'll let you take a look at it but maybe it belongs in the supplemental
%  \end{figure}

  The $z$-direction correlation functions show that layers in our model prefer
  to stack further apart than the 3.7 \angstrom~ suggested by experiment. We attempted equilibration 
  with layers stacked 4.0 $\nm$ apart and to our surprise, we observed
  long-term stability of a qualitatively different configurations suggesting
  that we have found more than one metastable free energy basin.
  %that the initial distance between layers can influence the approach towards 
  %equilibrium.
  \begin{itemize}
  	\item Equilibrated systems built according to the 3.7 \angstrom~layer spacing 
        implied by R-$\pi$ are characterized by a defined, cylindrical and open pore 
	structure.
        \item We will refer to this large set of configurations, with an open pore, as 
        the OP Basin (open pore) (Figure~\ref{fig:abasin}).
	\item Simulations of systems built with layers stacked greater than 4 
	\angstrom~ apart results in a pore structure characterized by high radial 
	disorder, while still maintaining partitioning between hydrophobic and 
	hydrophilic regions.
	\item This will be called the CP Basin (closed pore) (Figure~\ref{fig:bbasin}).
	\item This LLC membrane may exist in at least two metastable states.
	\item The distinct difference in pore structure exhibited by each phase will 
	likely lead to different transport mechanisms.
	\item Because the pore structure will vary between each Basin, understanding 
	which phase exists experimentally is necessary in order to ensure we are 
	studying the system which actually dominates.
  \end{itemize}

@@

  We answer question (3) by simulating X-ray diffraction patterns produced from
  equilibrated MD trajectories. We leave open the possibility that the 
  experimental structure might be reminiscent of the parallel displaced or sandwiched
  configurations in the OP or CP basins.
  %We created systems using three distinct initial configurations and examined
  %their structure by simulating X-ray diffraction patterns produced from equilibrated MD trajectories.
  \begin{itemize}
  	\item OP Basin systems were built in both the parallel displaced and sandwiched 
	configurations with an intial layer spacing of 3.7 \angstrom~.
	\item A third system was created by stacking layers in the sandwiched 
	configuration 5 \angstrom~apart in order to guide it towards the CP Basin.
	% BJC: I've done an additional offset disordered system which goes to Basin CP but I think that will confuse the point
	\item The three systems were equilibrated according to our procedure with
	NPT simulations of greater than 400 ns.
	\item Simulated diffration patterns were generated using portions of the
	trajectory after equilibration.  
	\item We assume the simulation has equilibrated when the distance between 
	pores and the membrane thickness stopped changing.
	\item Simulated diffraction patterns for all three structures are shown in 
	Figure ~\ref{fig:XRDsim}. 
  \end{itemize}

  % Three paragraphs instead here? Talk about disordered, parallel displaced and 
  % layered separately? Try it. 
  % Talk about disordered last so it leads in to 
  % Also maybe don't talk about question 4 until after this

  %Full comparison of experimental 2D WAXS with simulated X-ray diffraction
  %patterns shows the most consistency with the offset configuration in the OP basin.

  Simulated diffraction of the disordered pore structure in the both the sandwiched
  and parallel displaced configurations does not match the experimental pattern.
  \begin{itemize}
        \item The disordered pore structure exhibits R-alkanes and R-pores but R-helix,
	R-$\pi$ and R-spots are not present. 
        \item Due to low resolution, making out the individual spots of R-pores is
        challenging and can be validated with slightly better resolution upon full
        spherical integration of the 3D structure factor. However, the same
        information can be extracted by measuring the pore spacing as described earlier.
        %BJC: ^^^This can be more concise 
        \item Although the structure's diffraction pattern is very different from
        experiment, its long-term stability suggests that the structure is realistic.
	We will explore this further when addressing (4). 
  \end{itemize}

  Simulated XRD of the sandwiched configuration contains all experimental features
  except for R-helix.
  \begin{itemize}
        \item R-alkanes and R-pores appear in the expected locations.
        \item R-$\pi$ is also present, intersecting R-alkanes at a lower q value than
        in experiment. The rings prefer to stack $\approx 4.1 \angstrom$ apart as % update distance if needed
        opposed to 3.7 \angstrom~.
        \item Most notably, R-spots appears in the expected location, which suggests 
        that there is something intrinsic to closer packing that gives rise 
        to such features. 
  \end{itemize}

  The parallel displaced configuration results in a simulated XRD pattern with 
  the closest match to experiment. 
  \begin{itemize}
	\item It produces the only pattern that exhibits all major reflections
	\item R-alkanes, R-pores and R-$\pi$ appear as they do in the sandwiched configuration. 
	\item R-spots appears, however with a lower intensity relative to R-alkanes
        when compared to the sandwiched configuration.
        \item R-helix appears apparently due to the parallel displaced aromatic rings
        %BJC: Maybe a figure to explain why this happens
  \end{itemize}

@@

  The spots that appear in the simulated XRD pattern of the OP basin
  conformations are a result of the way alkane tails pack together.
  \begin{itemize}
  	\item Previously, the spots in the diffraction pattern had been explained 
	as the product of tilted alkane chains.
	\item We measured the tilt angle of the alkane chains and showed that our 
	system equilibrates to an average tilt angle close to zero degrees (See Supplemental Information). 
	\item To understand the origin of the spots, we determined which atoms gave rise to the feature
	\item Since R-spots is present as higher intensity spots within R-alkanes, it is likely
        that the spots arise as a consequence of the tails. 
	\item By removing atoms from the trajectory and simulating a diffraction 
	pattern, we were able to isolate the cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).
	\item Since the tails stay nearly flat, we plotted the centroids of the 
	tails and measured the angle between each centroid and its nearest neighbors
	with respect to the plane of the membrane (Figure~\ref{fig:centroids}).
	\item The distribution of these angles is consistent with the location of 
	the spots (Figure~\ref{fig:tail_packing}).
	\item The peaks of interest in Figures~\ref{fig:offset_tails}~and~\ref{fig:layered_tails}
	are located at $\pm$ 33 $\degree$ which is the same location where the highest intensity
	of spots are located on the simulated patterns (See Supplemental Information for quantitative proof)
	\item We integrated the raw experimental 2D WAXS data in the region bounding R-alkanes 
        and found the angle at which R-spots reaches its highest intensity to be $\pm$ 37 $\degree$ which 
        is a reconcilable difference with our simulated results.  
  \end{itemize}
